Turbulence in compact to giant H~II regions

### 2022-12-12 strucfunc_paper.tex
Javier changes 2022-12-11

Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs}g,
which shows how the fractional width of the probability distribution of
large-scale \ha{} surface brightness fluctuations
varies with the RMS turbulent Mach number, \Mach{},
of the three-dimensional velocity fluctuations.
The Mach number is estimated by assuming that the plane-of-sky velocity dispersion is
a good estimate of the turbulent fluctuations in one dimension
and that the turbulence is isotropic, yielding:
\(\Mach = \sqrt{3} \sigma\pos / \csound\),
where an ionized sound speed of \(\csound = \SI{11}{km.s^{-1}}\)
is assumed for all sources.
\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
The RMS fractional width of density fluctuations in a turbulent medium,
\(\shortsig{\rho} \equiv \longsig{\rho}\),
is predicted to depend linearly on the Mach number as
\(\shortsig{\rho} = b \Mach\),
where \(b\) depends on the nature of the turbulent driving \citep{Federrath:2010z},
varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
This is shown by gray shading\footnote{%
  In the figure, it is assumed that the relative fluctuations in surface brightness
  and density are equal, which is a result of the
  cancellation between two effects. First, that the volumetric \ha{} emissivity \(E\)
  is proportional to density squared, so that \(\shortsig{E} = 2 \shortsig{\rho}\). 
  Second, that fluctuations in surface brightness \(S\) are related to those in emissivity
  by \(\shortsig{S} = R^{1/2} \shortsig{E}\), where \(R\)
  is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
  For an emissivity power spectrum \(P(k) \sim k^{-3}\)
  and assuming a ratio of map size to correlation length
  of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
  we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\). 
}
in Figure~\ref{fig:brightness-pdfs}h,
where it can be seen that many of the sources with subsonic velocity dispersions
(\(\Mach < 1\)) fall to the right of the theoretical prediction,
implying that other factors in addition to turbulence are responsible for
producing the fluctuations in density and surface brightness in these regions
(see also section 4.5 of \citealp{arthur2016turbulence}).
For our highest luminosity source of 30~Dor on the other hand,
the velocity dispersion is clearly supersonic (\(\Mach \approx 2.7\))
and, although the surface brightness fluctuations are also larger than in the other sources,
they are consistent with being caused by turbulence-induced density fluctuations.

>>>>

Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs},
which shows how the fractional width of the probability distribution of
large-scale \ha{} surface brightness fluctuations
varies with the RMS turbulent Mach number, \Mach{},
of the three-dimensional velocity fluctuations.
The Mach number is estimated by assuming that the plane-of-sky velocity dispersion is
a good estimate of the turbulent fluctuations in one dimension
and that the turbulence is isotropic, yielding:
\(\Mach = \sqrt{3} \sigma\pos / \csound\),
where an ionized sound speed of \(\csound = \SI{11}{km.s^{-1}}\)
is assumed for all sources.
\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
The RMS fractional width of density fluctuations in a turbulent medium,
\(\shortsig{\rho} \equiv \longsig{\rho}\),
is predicted to depend linearly on the Mach number as
\(\shortsig{\rho} = b \Mach\),
where \(b\) depends on the nature of the turbulent driving \citep{Federrath:2010z},
varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
This is shown by gray shading\footnote{%
  In the figure, it is assumed that the relative fluctuations in surface brightness
  and density are equal, which is a result of the
  cancellation between two effects. First, that the volumetric \ha{} emissivity \(E\)
  is proportional to density squared, so that \(\shortsig{E} = 2 \shortsig{\rho}\). 
  Second, that fluctuations in surface brightness \(S\) are related to those in emissivity
  by \(\shortsig{S} = R^{1/2} \shortsig{E}\), where \(R\)
  is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
  For an emissivity power spectrum \(P(k) \sim k^{-3}\)
  and assuming a ratio of map size to correlation length
  of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
  we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\). 
}
in Figure~\ref{fig:brightness-pdfs}h,
where it can be seen that many of the sources with subsonic velocity dispersions
(\(\Mach < 1\)) fall to the right of the theoretical prediction,
implying that other factors in addition to turbulence are responsible for
producing the fluctuations in density and surface brightness in these regions
(see also section 4.5 of \citealp{arthur2016turbulence}).
For our highest luminosity source of 30~Dor on the other hand,
the velocity dispersion is clearly supersonic (\(\Mach \approx 2.7\))
and, although the surface brightness fluctuations are also larger than in the other sources,
they are consistent with being caused by turbulence-induced density fluctuations.
